Dissertation notes

### 2023-03-13 Texfiles/Notes.tex
Timeline of changes
new notes

    \item When did the changes take place?
    \item When were the changes announced?
\end{itemize}

>>>>

      \item \textbf{When did the changes take place?}

            First round in 2012 and a second round of changes in March 2014. Which age groups were particularly impacted?

      \item \textbf{When were the changes announced?}

            There were expected changes announced in March 2011. Unexpected changes made in March 2014.
            The changes made in 2011 would still have been quite unexpected so we could probably still expect changes in early retirement consumption.

            So perhaps we could look at people just above and just below the cut offs.
      \item \textbf{What were the pension rules before?}
            Were there cutoffs that changed peoples behaviour?

\end{itemize}
